---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dataREACHr

<!-- badges: start -->

<!-- badges: end -->

dataREACHr package contains tools to process data for Project REACH at
Penn State. Project REACH is a longitudinal study of the effects of food
marketing on children's eating behaviors and neural responses to food
cues. Data are collected from children and parents across 5 visits.

dataREACHr functions can:

-   organize data and meta-data (JSONS) for surveys (REDCap) and
    behavioral tasks into the [Brain Imaging Data
    Structure](https://bids.neuroimaging.io/)

-   parse text files from the RRV task into CSVs

-   generate group-level dataframes containing questionnaire,
    demographic, intake, and anthropometric data

-   generate subject-specific dataframes containing cleaned behavioral
    data

-   export bids-compliant TSVs and JSONS for survey and behavioral data

## Installation

You can install the development version of dataREACHr from
[GitHub](https://github.com/) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("bfuchs18/dataREACHr")
```

## Data organization

Using dataREACHr functions requires a directory structure of:

base_dir/ (user defined)

├── untouchedRaw/

├── bids/

│ ├── sourcedata/

│ \| ├── phenotype/

and dataREACHr functions will create:

base_dir/ (user defined)

├── bids/

│ ├── phenotype/

│ ├── rawdata/

## Processing data with dataREACHr

Primary user functions include:

-   **proc_redcap() -** processes visit and double-entry REDCap (survey)
    data in bids/sourcedata/phenotype, exports processed data into
    bids/phenotype

-   **qc_redcap() -** performs quality assessment checks on output of
    proc_redcap()

-   **proc_task() -** copies cognitive and behavioral task data from
    untouchedRaw/ to bids/sourcedata/, processes data and exports into
    bids/rawdata/

-   **proc_task_derivs() -** creates and exports summary databases for
    cognitive and behavioral tasks

The script used to process REACH data using the above dataREACHr
functions can be found
[here](https://github.com/bfuchs18/R01_Marketing/blob/master/ParticipantData/bids/code/beh_into_bids.R).

This README was generated from README.Rmd using
`devtools::build_readme()\`
