---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dataREACHr

<!-- badges: start -->
<!-- badges: end -->

dataREACHr package contains tools to process data for Project REACH at Penn State. This includes organizing multi-visit survey (REDCap), behavioral (e.g., cognitive task), and fmri-related data into the Brain Imaging Data Structure and generating meta-data (jsons).

dataREACHr functions can:
- copy behavioral data from untouchedRaw to bids/sourcedata
- parse text files from the RRV task into CSVs
- generate group-level dataframes containing questionnaire, demographic, intake, and anthropometric data
- generate subject-specific dataframes containing cleaned behavioral data
- export bids-compliant TSVs and JSONS for behavioral data into bids/rawdata/ and survey data into bids/phenotype

## Installation

You can install the development version of dataREACHr from [GitHub](https://github.com/) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("bfuchs18/dataREACHr")
```

## Processing data with dataREACHr

The two primary functions to process survey (redcap) and behavioral data are proc_redcap() and proc_task(), respectively.

Using these functions requires a directory structure of: 
      - base_dir (user defined)
         - **untouchedRaw**
         - **bids**
           - **sourcedata**
           - **rawdata**
           - **phenotype**

Below is a basic example of how to process survey and task data:

```{r example, eval=FALSE}
library(dataREACHr)

# define path to the base_dir directory (contains untouchedRaw/ and bids/ sub-directories)
base_dir = "/path/to/base_dir/"

# define names of redcap files to process
visit_file_name =  "visit_data.csv"
double_entry_file_name = "double_entry_data.csv"

#### process redcap data ####

# assign paths to data downloaded from redcap
visit_data_path = paste0(base_dir, "/bids/sourcedata/phenotype/", visit_file_name)
data_de_path = paste0(base_dir, "/bids/sourcedata/phenotype/", double_entry_file_name)

# process redcap data and export TSVs and JSONS into bids/; overwrite existing output
proc_redcap(visit_data_path, data_de_path, overwrite = TRUE)

#### process task data ####

# process task data and export TSVs and JSONS into bids/; overwrite existing files in rawdata for all tasks
proc_task(
  base_wd = base_dir,
  overwrite_parsed_rrv = FALSE,
  overwrite_sourcedata = FALSE,
  overwrite_rawdata_vector = c("all_tasks"),
  overwrite_jsons = FALSE
)


```

This .md file was generated from README.Rmd` using `devtools::build_readme()`
